---
title: "Game Day"
author: "Ken Lau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Game Day}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

### Introduction
Are you an NHL fan? Do you always have a difficult time looking up whether your favourite team is playing on a particular day, or the scores of NHL  games for any particular day? This package provides a simple method to check whether your favourite team is playing on a given day. In addition, you could look up the scores of all teams that play on a particular day if you are curious.

### Use Cases
#### Case Study 1
Say you want to find the dates your favourite NHL team will play in the next month.

```{r}
todayDate = as.Date("2014-11-19")
endDate = as.Date("2014-12-19")
# generate sequence of dates per day from today's date to next month
monthDates = strftime(seq(from=todayDate, to=endDate, by="day"))
# signify who your favourite team is
favouriteTeam = "Canucks"
# vector of booleans giving whether the team plays for each day
boolDates = unlist(lapply(monthDates, FUN=gday, team=favouriteTeam))
# returns a vector of dates of when your team will be playing in the next month
monthDates[boolDates]
```

#### Case Study 2
Following the last example, you can also generate the scores of your favourite team from the last month and compare scores for home vs away. Since there may be a difference in number of home and away games, we should probably take the average score per game.

```{r}
library(plyr)
library(dplyr)
library(ggplot2)

todayDate = as.Date("2014-11-19")
# Note that this is one month back from today's date
endDate = as.Date("2014-10-19")
favouriteTeam = "Canucks"
boolDates = unlist(lapply(monthDates, FUN=gday, team=favouriteTeam))
# returns a vector of dates of when your team will be playing in the next month
scoreDays = monthDates[boolDates]
scoresDf = ldply(scoreDays, .fun=scores)
homeScores = scoresDf %>% select(home, home_score) %>%
              filter(grepl(favouriteTeam, home, ignore.case=T)) %>%
              select(home_score)
homeAvg = mean(homeScores[,1])
awayScores = scoresDf %>% select(away, away_score) %>% 
              filter(grepl(favouriteTeam, away, ignore.case=T)) %>% 
              select(away_score)
awayAvg = mean(awayScores[,1])
ggData = data.frame("location"=c("home","away"), 
          "average_score"=c(homeAvg, awayAvg))
gg = ggplot(ggData, aes(x=location, y=average_score)) + 
      geom_bar(stat="identity", width=.5) + 
      ggtitle("Average scores")
```
```{r results='asis'}
gg
```


